% Dionysia Theofylaktou Professional CV - 2025
\documentclass[a4paper,11pt]{article}

\usepackage[a4paper,top=0.5cm, bottom=0.5cm, left=1.0cm, right=1.0cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{ragged2e}

% Define colors
\definecolor{primary}{HTML}{2c3e50}
\definecolor{secondary}{HTML}{34495e}
\definecolor{accent}{HTML}{3498db}

% Configure hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent,
    pdfborder={0 0 0}
}

% Configure sections with better styling
\titleformat{\section}
    {\Large\bfseries\color{primary}}
    {\thesection}{0em}{}
    [\vspace{-0.5em}\textcolor{accent}{\titlerule[0.8pt]}\vspace{-0.1em}]
\titlespacing{\section}{0pt}{2pt}{1pt}

% Define new column type for better text spacing
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X}

% Remove page numbers
\pagenumbering{gobble}

\begin{document}

% Header with improved styling
\begin{center}
    {\Huge\bfseries\color{primary} Dionysia Theofylaktou}\\[0.15em]
    {\large\color{secondary} Java Developer | Backend \& Mobile Development}\\[0.25em]
    \textcolor{secondary}{
        Athens, Greece $\cdot$
        \href{tel:+306979534975}{\faPhone~+30 697 953 4975} $\cdot$
        \href{mailto:dtheofylaktou@gmail.com}{\faEnvelope~dtheofylaktou@gmail.com} $\cdot$
        \href{https://www.linkedin.com/in/dionysia-theofylaktou/}{\faLinkedin~linkedin.com/in/dionysia-theofylaktou} $\cdot$
        \href{https://github.com/dioni-theof}{\faGithub~github.com/dioni-theof}
    }
\end{center}

\vspace{0.15em}

\section*{Professional Summary}
\textit{Computer Science graduate transitioning from education to software engineering. Holds an M.Sc. in Advanced Informatics and Computing Systems with hands-on experience in Java, Spring Boot, and Android/mobile development gained through academic studies and recent projects.}

\vspace{0.2em}

\section*{Technical Skills \& Languages}
\noindent
\begin{minipage}[t]{0.49\textwidth}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, parsep=1pt, partopsep=0pt]
    \item \textbf{Core Technologies:} Android~SDK, Spring~Boot, Java, Python, Hibernate, JPA
    \item \textbf{{Databases \& Cloud:}} MySQL, PostgreSQL, NoSQL, Cloud~Firestore, Firebase
    \item \textbf{{Languages:}} Greek~(Native), English~(Professional)
\end{itemize}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\textwidth}
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt, parsep=1pt, partopsep=0pt]
    \item \textbf{{Networking:}} TCP/IP, UDP, DNS, DHCP
    \item \textbf{{Development Tools:}} Maven, Docker, Git, UML, IntelliJ
    \item \textbf{{Architecture:}} RESTful~APIs, Microservices, Design~Patterns
\end{itemize}
\end{minipage}

\vspace{0.2em}

\section*{Education}
\begin{tabularx}{\textwidth}{@{}l Y@{}}
\textbf{\textcolor{primary}{2019 - 2022}} & \textbf{M.Sc. Advanced Informatics and Computing Systems} \textbar\space \textbf{University of Piraeus} \\
& \textit{Grade: \textbf{\textcolor{accent}{9.03/10}} \textbullet\space Specialization: Advanced Software Development Technologies} \\[0.15em]

\textbf{\textcolor{primary}{2008 - 2019}} & \textbf{Diploma Applied Mathematical and Physical Sciences} \textbar\space \textbf{NTUA} \\
& \textit{Grade: 6.5/10 \textbullet\space Major: Engineering Physics}
\end{tabularx}

\vspace{0.2em}

\section*{Research Projects \& Publications}

\begin{tabularx}{\textwidth}{@{}l Y@{}}
\textbf{\textcolor{primary}{2018 - 2019}} & \textbf{Computational Application for Natural Products Database} \textbar\space \textit{NTUA} \\
& Platform analyzing 562~research articles, 87~organisms, 105~target genes. NoSQL/Firebase. \href{https://doi.org/10.1155/2021/9993518}{\textcolor{accent}{https://doi.org/10.1155/2021/9993518}} \\[0.15em]

\textbf{\textcolor{primary}{2021 - 2022}} & \textbf{Personalized ID using European Blockchain Infrastructure} \textbar\space \textit{University of Piraeus} \\
& Blockchain identity management with Self-Sovereign Identity and verifiable credentials. \href{https://dione.lib.unipi.gr/xmlui/handle/unipi/14917}{\textcolor{accent}{https://dione.lib.unipi.gr/xmlui/handle/unipi/14917}} \\
\end{tabularx}

\vspace{0.2em}

\section*{Personal Projects}

\begin{tabularx}{\textwidth}{@{}l Y@{}}
\textbf{\textcolor{primary}{2025}} & \textbf{Course Management System} \textbar\space \textit{Spring Boot \& PostgreSQL} \\
& RESTful API with Java 21, Spring Boot 3.4.5, CRUD operations, course enrollment, pagination, OpenAPI. \href{https://github.com/dioni-theof/course-management}{\textcolor{accent}{github.com/dioni-theof/course-management}} \\[0.15em]

\textbf{\textcolor{primary}{2025}} & \textbf{Reservation System} \textbar\space \textit{Spring Boot \& PostgreSQL} \\
& Booking management with Java 21, resource tracking, scheduling APIs, capacity management. \href{https://github.com/dioni-theof/reservation-system}{\textcolor{accent}{github.com/dioni-theof/reservation-system}} \\[0.15em]

\textbf{\textcolor{primary}{2025}} & \textbf{SmartAlert Emergency Mobile App} \textbar\space \textit{Android \& Firebase} \\
& Emergency alert app with fire/fall detection, automatic SOS, multilingual support, Java 11. \href{https://github.com/dioni-theof/smart-alert}{\textcolor{accent}{github.com/dioni-theof/smart-alert}} \\
\end{tabularx}

\vspace{0.2em}

\section*{Work Experience}

\begin{tabularx}{\textwidth}{@{}l Y@{}}
\textbf{\textcolor{primary}{2024 - 2025}} & \textbf{Computer Science \& Networks Instructor} \textbar\space \textit{Karakaxis (EPAL), Greece} \\
& Taught Python programming and Computer Networks (TCP/IP, UDP, DNS, DHCP, Routing). 4 students scored 90\%+ in national exams. \\[0.12em]

\textbf{\textcolor{primary}{2023 - 2024}} & \textbf{Computer Science \& Physics Teacher} \textbar\space \textit{Diakrotima, Greece} \\
& Delivered algorithms and pseudocode curriculum to final-year students. Developed lesson plans and supported national exam preparation. \\[0.12em]

\textbf{\textcolor{primary}{2021 - 2023}} & \textbf{Academic Lead – Science Subjects} \textbar\space \textit{Mikro Panepistimio, Greece} \\
& Led curriculum development, implemented data-driven progress tracking, managed personalized learning plans across multiple levels. \\[0.12em]

\textbf{\textcolor{primary}{2019 - 2020}} & \textbf{STEM Instructor} \textbar\space \textit{Mouseio Peiramaton, Greece} \\
& Designed hands-on programming activities with LEGO® Education kits. Taught mechanics, electronics, and problem-solving principles. \\
\end{tabularx}

\end{document}